%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Thomas} % Your first name
\familyname{Funck} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{3801 Rue University}{Montreal, QC H3A 2B4}
\mobile{(514) 566 6192}
\email{thomas.funck@mail.mcgill.ca}


%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2014--}{PhD Neuroscience}{McGill University}{Montreal}{\textit{GPA -- 3.88}}{}
\cventry{2011--2013}{MSc Neuroscience}{McGill University}{Montreal}{\textit{GPA -- 4.0}}{}
\cventry{2006--2010}{BA Philosophy}{McGill University}{Montreal}{\textit{GPA --  3.6}}{First Class Honours}

\section{PhD Thesis}
\cvitem{Title}{\emph{Measuring neuronal density in the living brain with high-resolution PET}}
\cvitem{Supervisors}{Alexander Thiel, MD, PhD, and Alan C. Evans, PhD}


\section{Masters Thesis}
\cvitem{Title}{\emph{Partial-volume correction for high-resolution positron emission tomography using cortical surface information}}
\cvitem{Supervisors}{Professor Alexander Thiel, MD, PhD}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching Experience}

\cventry{2015}{Teaching assistant}{INDS 212: Human Behaviour}{McGill University}{Neuroanatomy and human brain dissection class for medical students}{}

\cventry{2016}{Teaching assistant}{INDS 212: Human Behaviour}{McGill University}{Neuroanatomy and human brain dissection class for medical students}{}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}
\cvitem{2010}{Force Avenir -- Health Award for Model World Health Organization  2010}
\cvitem{2014}{1st Place Poster Award -- Society for Nuclear Medicine and Molecular Imaging}




%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{Conference Abstracts}

\cvitem{2012}{Funck T, Zepper P, Evans A, Thiel A. Cortical Thickness-Based Partial Volume Correction for High Resolution PET. In: Organization for Human Brain Mapping. Beijing}
\cvitem{2013}{Funck T, Evans A, Thiel A. Cortical surface-based partial volume correction for high-resolution brain PET images. Soc Nucl Med Annu Meet Abstr. 2013;54(Supplement 2):2064}
\cvitem{2014}{Funck T, Paquette C, Evans A, Thiel A. Effect of partial-volume correction on binding potential in high-resolution PET. J Nucl Med. 2014;55(Supplement 1):2031}
\cvitem{2014}{Paquette C, Funck T, Sidel M, Melmed C, Monchi O, Thiel A. Up-regulation of cortical GABA-A receptors in idiopathic Parkinson's syndrome with dyskinesia. J Nucl Med.
55(Supplement 1):1828}	

\cvitem{2015}{Zepper P, Funck T, la Fougere C, Kostikov A, Schirrmacher R, Thiel A. Imaging delayed cell death in subacute stroke with high-resolution 18F-Flumazenil. Soc Nucl Med Annu Meet Abstr. 2012;53(Supplement 1):37.}

\cvitem{2016}{Funck T, Al-Kuwaiti M, Schipper J, Lepage C, Evans AC, Thiel A. Measuring selective neuronal loss with high resolution PET. In: Organization for Human Brain Mapping. Geneva.}

\section{Publications}

\cvitem{2014}{Funck T, Paquette C, Evans A, Thiel A. Surface-based partial-volume correction for high-resolution PET. Neuroimage. 2014;102:674-687}

\cvitem{2015}{Schirrmacher R, Dea M, Heiss WD, Kostikov A, *Funck T, Quessy S, Bedell B, Dancause N and Thiel A. Which aspects of stroke do animal models capture? A multitracer micro-PET study of focal ischemia. Cerebrovascular Disease 2015}

\cvitem{In Press}{Funck, T. Al-Kuwaiti, M., Lepage, C., Zepper, P., Minuk, J., Schipper, H.M., Evans, A.C., Thiel. Assessing neuronal density in peri-infarct cortex with PET: effects of cortical topology and  partial volume correction. Human Brain Mapping}

\cvitem{In Review}{Pomares, F, Pomares, F., Roy, S., Daigle-Martel, A., Ceko, M., Narayanan, S., Araujo, D., Thiel, A., Stikov, N., Fitzcharles, M., Schweinhardt, P. Multimodal brain imaging indicates distinct origin of altered regional grey matter in chronic pain. Journal of Neuroscience}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer skills}

\cvitem{Basic}{Haskell}
\cvitem{Intermediate}{Matlab, Linux, R}
\cvitem{Advanced}{C, Python, Bash}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{French}{Fluent}{}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage





%----------------------------------------------------------------------------------------

\end{document}
